A Reduced Order Model for Porous Media Flows: Coupling Linear Regression with Principal Component Analysis (PCA) using High-Order Singular Value Decomposition (HOSVD) in Upscaling Calculations for Permeability in Reservoir Simulations

### 2018-12-03 Papers/AppliedMaths2018/Resubmission/Stochastic_Upscaling_UK_AMM_2018b.tex
files to be modified in the next 250min
updates

\subsection{Model Description}\label{subsection:model}
The BaseCase  (\ie high-resolution mesh) model for the permeability field builds on the $2 \times 2$ block, $4$ quadrant model used initially by \citet{Cardwell_1945} and later by \citet{Yeo2001} and \citet{dawe_2008}. These authors designed the permeability field for the quadrants in a checker-board style which means that diagonally opposite blocks retained the same permeability values with one set of diagonally opposite blocks having a higher permeability value compared to the other set. Hence, one set of diagonally opposite blocks are referred to as high permeability blocks while the other set is referred to as low permeability blocks.

The BaseCase permeability model used here retains the checkerboard desgined used by the recently named authors. Albeit, the permeability dataset for each block in the set of diagonally opposite blocks have similar value (\ie not exactly the same as in the papers referred to), although one set can still be referred to as a set of high permeability blocks while the other set is referred to as a set of low permeability blocks. Furthermore, within each block, the permeability field varies within a pre-defined range and consists of $1600$ permeability values. More details on the design of the permeability field for the BaseCase is available in section~\ref{subsubsection:basecase_preprocess_algorithm}. Figures~\ref{fig:PermFields}a and~\ref{fig:PermFields}b give a pictorial representation of the permeability field for the base case with the mesh discretization visible and invisible, respectively.  Using the labelling scheme used by \citet{dawe_2008}, the quadrant model block $K1,~K2,~K3$ and $K4$ are top left, bottom left, top right and bottom right, respectively.

>>>>

\subsection{Model Description}\label{subsection:model}
The BaseCase  (\ie high-resolution mesh) configuration for the permeability dataset builds on the $2 \times 2$ block, \ie $4$ quadrant model orginally used by \citet{Cardwell_1945} and later by \citet{Yeo2001} and \citet{dawe_2008}. In the domain designed by these authors, permeability is represented as checker-board in which diagonally opposite blocks retained the same permeability values with one set of diagonally opposite blocks having a higher permeability value compared to the other set. Hence, one set of diagonally opposite blocks are referred to as high permeability blocks while the other set is referred to as low permeability blocks.

The BaseCase permeability model used here retains the checkerboard desgined used by the recently named authors. Albeit, the permeability dataset for each block in the set of diagonally opposite blocks have similar value (\ie not exactly the same as in the papers referred to), although one set can still be referred to as a set of high permeability blocks while the other set is referred to as a set of low permeability blocks. Furthermore, within each block, the permeability field varies within a pre-defined range and consists of $1600$ permeability values. More details on the design of the permeability field for the BaseCase is described in Section~\ref{subsubsection:basecase_preprocess_algorithm}. Figures~\ref{fig:PermFields}a and~\ref{fig:PermFields}b give a pictorial representation of the permeability field for the base case with the mesh discretization visible and invisible, respectively.  Using the labelling scheme used by \citet{dawe_2008}, the quadrant model block $K1,~K2,~K3$ and $K4$ are top left, bottom left, top right and bottom right, respectively.
